---
title: "esm206_lab8"
author: "Eva Wilson"
date: "11/15/2021"
output: html_document
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages:
library(here)
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
```

```{r}
# Read in the data:
homes <- read.csv(here("data", "slo_homes.csv"))
```

Make a subset called homes_sub that only contains observations (rows) where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo",
         "Arroyo Grande",
         "Atascadero",
         "Santa Maria-Orcutt"))
```

Summary statistics (home price, based on city and sale status):

- Find and return in a nice summary table the mean and the standard deviation of home price, grouped by city and sale status.

```{r, include = FALSE, eval = FALSE}

# Note - eval = FALSE, does not even evaluate code (likely because it takes so long, or because you are trying to troubleshoot one line of code at a time to figure out what is going wrong)

homes_summary <- homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))

ggplot(homes_sub, aes(x = Price)) + # Similar to histogram, just uses kernal smoothing to see measure of densities
  geom_density(aes(color = City, fill = City), alpha = 0.2)+
  scale_x_continuous(limits = c(0, 3e6)) # generic function to change the conditions about the x axis if it is a continuous variable
```

Explore the relationship (visual data exploration) between square footage and home price. 
Change the point color by city, and the point shape by sale status.
```{r}
ggplot(homes_sub, aes(x = SqFt, y = Price)) +
  geom_point(aes(color = City, shape = Status)) +
  geom_smooth(method = lm)
```

## Model relationship with home price as DV

```{r}
# This is a saturated model because it includes so many variables

homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, 
                data = homes_sub)

# Make a subset that only contains the quantitative variables
homes_quant <- homes_sub %>% 
  select(Price:PricePerSqFt)

homes_cor <- cor(homes_quant)
homes_cor # Shows you the correlation between these variables. Hopefully, it is a strong positive correlation 

corrplot(homes_cor, method = 'ellipse') # This is a visual representation of the information above

# How would I explore diagnostic plots?
plot(homes_lm1)
```

Try another model where we simplify this a bit:

- City
- SqFt
- Status 

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, 
                data = homes_sub)

# Or just call this in the console
homes_lm2

plot(homes_lm2)
```

Find the AIC value of each model:

```{r}
AIC(homes_lm1)
AIC(homes_lm2)
```

Try another permutation of this model that you think might make sense, check out and compare the model fit, outputs and AIC value.

```{r}

homes_lm3 <- lm(Price ~ City + SqFt + Status + Bedrooms, 
                data = homes_sub)

homes_lm3
plot(homes_lm3)
AIC(homes_lm3)
```

Use `modelsummary` to show model outputs side-by-side:


If you use modelsummary to return model outputs of multiple models, it wants you to feed it to it as a list.

```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

## Start making predictions with this model 


Use `broom::augment()` 

```{r}
homes_predicted <- augment(homes_lm1)
```

Use the `predict()` function to try out your model on new scenarios that you create. 


