---
title: "esm206_lab8"
author: "Eva Wilson"
date: "11/15/2021"
output: html_document
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages:
library(here)
library(tidyverse)
library(janitor)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
```

```{r}
# Read in the data:
homes <- read.csv(here("data", "slo_homes.csv"))
```

Make a subset called homes_sub that only contains observations (rows) where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo",
         "Arroyo Grande",
         "Atascadero",
         "Santa Maria-Orcutt"))
```

Summary statistics (home price, based on city and sale status):

- Find and return in a nice summary table the mean and the standard deviation of home price, grouped by city and sale status.

```{r, include = FALSE, eval = FALSE}

# Note - eval = FALSE, does not even evaluate code (likely because it takes so long, or because you are trying to troubleshoot one line of code at a time to figure out what is going wrong)

homes_summary <- homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))

ggplot(homes_sub, aes(x = Price)) + # Similar to histogram, just uses kernal smoothing to see measure of densities
  geom_density(aes(color = City, fill = City), alpha = 0.2)+
  scale_x_continuous(limits = c(0, 3e6)) # generic function to change the conditions about the x axis if it is a continuous variable
```

Explore the relationship (visual data exploration) between square footage and home price. 
Change the point color by city, and the point shape by sale status.
```{r}
ggplot(homes_sub, aes(x = SqFt, y = Price)) +
  geom_point(aes(color = City, shape = Status))
```

